Computing the bicharacter of huge subspaces of polynomials

### 2019-07-05 article/article.tex
Add comments

	When $k=1$, the action of $GL_1$ is trivial; $R_{\Sn}$ is of dimension $n!$ and carries the usual graded representation of $\Sn$. Its character is given by a Hall-Littlewood polynomial.
	When $k=2$, $R_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), the bigraded character is a Macdonald polynomial.

>>>>

	When $r=1$, the action of $GL_1$ is trivial; $R_{\Sn}$ is of dimension $n!$ and carries the usual graded representation of $\Sn$. Its character is given by a Hall-Littlewood polynomial.
	When $r=2$, $R_{\Sn}$ is of dimension $(n+1)^{n-1}$ ($16807$ for $n=6$); as a consequence of Haiman's proof of the $n!$-conjecture (see \cite{Haiman2002}), the bigraded character is a Macdonald polynomial.
